RationalGRL: A Framework for Argumentation and Goal Modeling

### 2017-02-05 formalframework.tex
formal framework

\begin{algorithm}[h]
  \caption{Answering CQ5b: ``Does goal $G$ decompose into any other tasks?'' With: ``Yes, namey into tasks $t_{n+1},\ldots,t_k$''}\label{alg:cq5b}
  \begin{algorithmic}[1]
    \Procedure{CQ5b}{$g_{id},\{i_1,\ldots,i_n\}, type, \{t_1,\ldots,t_k\}$}
    \State $T_{id} = \{i_1,\ldots,i_n\}$
    \For{$t_i$ in $\{t_1,\ldots,t_k\}$}\label{alg:cq5b:for1}
      \If{$\exists_{A\in Args} \{task(t_{id}),name(t_{id},t_i)\}\subseteq A$}
        \State $T_{id} \gets T_{id} \cup \{t_{id}\}$
      \Else
        \State $id\gets id+1$
        \State $A \gets \{task(id),name(id,t_i)\}$
        \State $Args \gets Args\cup A$
        \State $T_{id} \gets T_{id} \cup \{id\}$
      \EndIf
    \EndFor
    \State $id\gets id+1$
    \State $A_{new} = \{decomp(id, g_{id}, T_{id}, type)\}$\label{alg:cq5b:newarg}
    \For{$A$ in $\{decomp(d,g_{id},x,y)\}\subseteq A\mid A\in Args\}$}\label{alg:cq5b:for2}
      \State $Att\gets Att \cup \{(A_{new},A)\}$
    \EndFor
    \State $Args \gets Args \cup \{A_{new}\}$
    \EndProcedure
  \end{algorithmic}
\end{algorithm}

@@

>>>>

\begin{algorithm}[h]
  \caption{Answering CQ5b: ``Does goal $G$ decompose into any other tasks?'' With: ``Yes, namey into tasks $t_1,\ldots,t_k$''}\label{alg:cq5b}
  \begin{algorithmic}[1]
    \Procedure{CQ5b}{$g_{id},\{i_1,\ldots,i_n\}, type, \{t_1,\ldots,t_k\}$}
    \State $T_{id} = \{i_1,\ldots,i_n\}$
    \For{$t_i$ in $\{t_1,\ldots,t_k\}$}\label{alg:cq5b:for1}
      \If{$\exists_{A\in Args} \{task(t_{id}),name(t_{id},t_i)\}\subseteq A$}
        \State $T_{id} \gets T_{id} \cup \{t_{id}\}$
      \Else
        \State $id\gets id+1$
        \State $A \gets \{task(id),name(id,t_i)\}$
        \State $Args \gets Args\cup A$
        \State $T_{id} \gets T_{id} \cup \{id\}$
      \EndIf
    \EndFor
    \State $id\gets id+1$
    \State $A_{new} = \{decomp(id, g_{id}, T_{id}, type)\}$\label{alg:cq5b:newarg}
    \For{$A$ in $\{decomp(\_,g_{id},\_,\_)\}\subseteq A\mid A\in Args\}$}\label{alg:cq5b:for2}
      \State $Att\gets Att \cup \{(A_{new},A)\}$
    \EndFor
    \State $Args \gets Args \cup \{A_{new}\}$
    \EndProcedure
  \end{algorithmic}
\end{algorithm}

@@

\todo{Marc}{Marc}{Do links need identifiers??}
